Verifying Demonstrations

### 2018-05-29 paper/SystemModel.tex

% cause identifier
\NewVariable{\cid}{cid}

@@

% protest
\NewVariable{\prtst}{P}
% subprotest
\NewVariable{\sprtst}{p}

@@

% proof share
\NewVariable{\psh}{s}
% proof shares
\NewVariable{\pshs}{S}
% protester identifier
\NewVariable{\pid}{pid}
% witness identifier
\NewVariable{\wid}{wid}

\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a 
  tuple where:
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); 
  and
  \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
  We say that \(\psh\) is part of a subprotest \(p = (\cid', t', l')\) iff 
  \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by \(\psh 
    \sqsubseteq p\).
  We let \(\pshs\) be the set of all proof shares.
\end{definition}
\sonja{do the same pair of people (witness-protester) get the
same wid on a different protest? The pid is unique for protester-cid
pair thus the id of a protester at a particular protest. Pid is thus
derived from the protester id (which has no term) and the protest id
(cid)? In analogy, wid is derived from pid (and thus cid) of both
participants, protesters i and j, say, where i witnesses j at cid and
simultaneously symmetrically j witnesses i?
\daniel{Not necessarily.}
Using wid and w is confusing since we changed the terminology to use
proof shares instead of the previous witness (as in testimony, not
person). wid sounds like it would be the id of the witness person,
pid sounds like it would be the id of the protester being witnessed,
we have defined neither and they might not be needed, but it is
confusing to read.}
\daniel{I made some minor changes, any better?}

@@

% proof
\NewVariable{\prf}{\pi}
% proofs
\NewVariable{\prfs}{\Pi}

>>>>

@@

@@

\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a 
  tuple where:
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); 
  and
  \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
  We say that \(\psh\) is part of a subprotest \(p = (\cid', t', l')\) iff 
  \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by \(\psh 
    \sqsubseteq p\).
  We let \(\pshs\) be the set of all proof shares.
\end{definition}

@@
